Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-11-20 papers/integration/omm_integ.tex
Current work in progress, Mon morning switching from laptop to desktop

% Section - description of biomechanical model
\subsection{biomechanical eye} \label{sec:methods:eye}

@@

% KM
An illustration of the biomechanical eye model is given in
Figure \ref{fig:eye_muscles}, while Figure \ref{fig:eye_head} depicts
the head model used in the proposed framework.

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/bio_eye1.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_muscles} Figure \arabic{figure}.}
{Example of the biomechanical eye model.}
\end{figure}

@@

% KM
Two types of muscle models of different complexity are supported. The
first models muscles using linear path actuators. This simplistic
model of ideal muscles can be easily integrated with high level brain
models. As described above the muscles are wrapped around the eye.
The more complex model supported is based on the Thelen model
[Thelen_ref.ris] that is also supported by OpenSim and implements
Hill-type muscles. It includes realistic muscle wrapping geometric
entities of the muscle fibers, while it accommodates for both
activation and contraction dynamics.  The dynamics of muscular forces
can be split into: 1) The elasticity of the muscles. 2) A delay
between the onset of the afferent excitatory signal and the actual
muscle contraction, caused by the transmission time of the action
potentials and by the necessary calcium release at the muscle fibres.

%EOM dynamics
The force applied by EOMs is controlled by an excitatory signal
supplied by motoneurons in the brainstem. The neural drive to produce
a saccadic eye movement can be characterized by a pulse component to
overcome the viscoelasticity of the orbital plant, a step component to
stabilize the eye in the new position, and a slide component that
models the gradual transition between the pulse and step.

@@

% KM
Finally, numerical integration of the biomechanical eye model is based
on the Kutta-Merson integration method.

% KM
Figure \ref{fig:eye_sim0} illustrates an example of the experimental
set-up of the proposed framework, while Figures \ref{fig:eye_sim1}
and \ref{fig:eye_sim2} depict the developed eye oculomotor simulation
system.

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Eye_sim0.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_sim0} Figure \arabic{figure}.}
{Example of the experimental set-up.}
\end{figure}

@@

% Section - description of the integration. scientific and
% technical. Already
\subsection{Integrating the models and closing the loop}
\label{sec:methods:integrating}

>>>>

% Section - description of biomechanical model
\subsection{Biomechanical eye} \label{sec:methods:eye}

@@

% KM
\rvwt{An illustration of the biomechanical eye model is given in
Figure \ref{fig:eye_muscles}, while Figure \ref{fig:eye_head} depicts
the head model used in the proposed framework.}

% To be moved in due course
\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/bio_eye1.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_muscles} Figure \arabic{figure}.}
{Example of the biomechanical eye model.}
\end{figure}

@@

% KM
\rvwt{Two types of muscle models of different complexity are supported. The
first models muscles using linear path actuators. This simplistic
model of ideal muscles can be easily integrated with high level brain
models. As described above the muscles are wrapped around the eye.
The more complex model supported is based on the Thelen model
\citep{thelen_adjustment_2003} that is also supported by OpenSim and implements
Hill-type muscles. It includes realistic muscle wrapping geometric
entities of the muscle fibers, while it accommodates for both
activation and contraction dynamics.  The dynamics of muscular forces
can be split into: 1) The elasticity of the muscles. 2) A delay
between the onset of the afferent excitatory signal and the actual
muscle contraction, caused by the transmission time of the action
potentials and by the necessary calcium release at the muscle fibres.}

% EOM dynamics
The force applied by EOMs is controlled by an excitatory signal
supplied by motoneurons in the brainstem. The neural drive to produce
a saccadic eye movement can be characterized by a pulse component to
overcome the viscoelasticity of the orbital plant, a step component to
stabilize the eye in the new position, and a slide component that
models the gradual transition between the pulse and step.

@@

% KM
\rvwt{Finally, numerical integration of the biomechanical eye model is based
on the Kutta-Merson integration method.}

% KM
\rvwt{Figure \ref{fig:eye_sim0} illustrates an example of the experimental
set-up of the proposed framework, while Figures \ref{fig:eye_sim1}
and \ref{fig:eye_sim2} depict the developed eye oculomotor simulation
system.}

% Figures to merge together into a single panel or move.
\begin{figure}[htb!]
\begin{center}
\includegraphics[width=0.5\textwidth]{./figures/Eye_sim0.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:eye_sim0} Figure \arabic{figure}.}
{Example of the experimental set-up.}
\end{figure}

@@

% Section - description of the integration. scientific and
% technical.
\subsection{Integrating the models and closing the loop}
\label{sec:methods:integrating}
